Simulations

### 2020-12-09 Simulations.Rmd
Fix algorithm

  top8 <- rbind(atlantic[1:2,],northeast[1:2,],southeast[1:2,],wildcards[1:2,])
  top8 = top8[order(-top8$totalPoints),]

  return(rbind(top8, wildcards[3:9,]))
}

@@

  top8 <- rbind(central[1:2,],northwest[1:2,],pacific[1:2,],wildcards[1:2,])
  top8 = top8[order(-top8$totalPoints),]

  return(rbind(top8, wildcards[3:9,]))
}

@@

  top8 <- rbind(metro[1:3,],atlantic[1:3,],wildcards[1:2,])
  top8 = top8[order(-top8$totalPoints),]

  return(rbind(top8, wildcards[3:10,]))
}

@@

  top8 <- rbind(central[1:3,],pacific[1:3,],wildcards[1:2,])
  top8 = top8[order(-top8$totalPoints),]

  return(rbind(top8, wildcards[3:8,]))
}
```

>>>>

  top6 <- rbind(atlantic[1:2,],northeast[1:2,],southeast[1:2,])
  top6 = top6[order(-top6$totalPoints),]

  return(rbind(top6, wildcards))
}

@@

  top6 <- rbind(central[1:2,],northwest[1:2,],pacific[1:2,])
  top6 = top6[order(-top6$totalPoints),]

  return(rbind(top6, wildcards))
}

@@

  top6 <- rbind(metro[1:3,],atlantic[1:3,])
  top6 = top6[order(-top6$totalPoints),]

  return(rbind(top6, wildcards))
}

@@

  top6 <- rbind(central[1:3,],pacific[1:3,])
  top6 = top6[order(-top$totalPoints),]

  return(rbind(top6, wildcards))
}
```
